Exploring mathematical objects from custom-tailored mathematical universes

### 2018-06-08 slides-filmat2018.tex
Beginning on notes slides for the FilMat talk

\IfSubStr{\jobname}{\detokenize{nonotes}}{
  \setbeameroption{hide notes}
}{
  \setbeameroption{show notes}
}
\setbeamertemplate{note page}[plain]
\setbeameroption{hide notes}

@@

>>>>

\setbeamertemplate{note page}[plain]
\setbeameroption{show notes}

@@

\note{\justifying
  The concept of a platonic heaven, where the
  objects live which mathematicians study, can be mathematically realized by
  the topos~$\Set$. As a category, it consists of all sets and all maps between
  these sets.

  But besides~$\Set$, there are many more toposes. Each such topos can be
  thought of as a mathematical universe, containing their own versions of the
  natural numbers,
}
